Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-05 docs/ms.tex
Update ms.tex

Our approach is to use an exceedingly flexible model for intrinsic
shape distribution, and assumes all the galaxies in different patches
abeys such a distribution. Then we can calculate the joint likelihood
of shpape distribution parameters and shears in different sky patches.With
a classical Gibbs MCMC sampler we are able to sample their posteior
distriibution.After marginalizing the shape parameters, we can obtain
the posterior distribution of shear,which we are interested in. This
approach allows us use the information maximumly without introducing
in any wrong assumption on intrinsic shape distribution.

>>>>

Our approach is to use an exceedingly flexible model for intrinsic
shape distribution, and assumes all the galaxies in different patches
abeys such a distribution. Then we can calculate the joint likelihood
of shpape distribution parameters and shears in different sky patches.With
a classical Gibbs MCMC sampler we are able to sample their posterior
distribution.After marginalizing the shape parameters, we can obtain
the posterior distribution of shear,which we are interested in. This
approach allows us use the information maximumly without introducing
in any wrong assumption on intrinsic shape distribution.
